### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/high_sim.tex
no message

This assumption assigns costs in descending order to the categories ``region around airports'', ``cities'', ``water'', and ``other''. Flying a UAV in each category is more costly by a factor of $b$ compared to the next most important category. The factor $b$ is a tuning parameter that we adjusted to vary the relative importance of the different categories, and we used $b=4$ in the figures below.

Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function. The region enclosed by the black boundary represent ``regoin around airports'', which have the highest cost. The dark blue, yellow, and light blue regions represent the ``cities'', the ``water'', and the ``other''' categories, respectively. We assumed that the origin corresponds to the city ``Concord'', and chose a number of other major cities as destinations.

>>>>

This assumption assigns costs in descending order to the categories ``region around airports'', ``cities'', ``other'', and ``water''. Flying a UAV in each category is more costly by a factor of $b$ compared to the next most important category. The factor $b$ is a tuning parameter that we adjusted to vary the relative importance of the different categories, and we used $b=4$ in the figures below.

Figure \ref{fig:airHighway_results} shows the San Francisco Bay Area (geographic) map, cost map, cost-minimizing paths, and contours of the value function. The region enclosed by the black boundary represent ``region around airports'', which have the highest cost. The dark blue, yellow, and light blue regions represent the ``cities'', the ``water'', and the ``other''' categories, respectively. We assumed that the origin corresponds to the city ``Concord'', and chose a number of other major cities as destinations.

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/introduction.tex
no message

In order to accommodate potentially thousands of vehicles simultaneously flying in the air, additional structure is needed to allow for tractable analysis and intuitive monitoring. An air highway system on which platoons of vehicles travel accomplishes both goals. However, many details of such a concept need to be addressed. Due to the flexibility of placing air highways compared to building ground highways in terms of highway location, even the problem of air highway placement can be daunting task. To address this, in the first part of this paper, we propose a flexible and computationally efficient way based on \cite{Sethian96} to perform optimal air highway replacement given an arbitrary cost map that captures the desirability of having UAVs fly over any geographical location. We demonstrate our method using the San Francisco Bay Area as an example. Once air highways are in place, platoons of UAVs can then fly in fixed formations along the highway to get from origin to destination.

>>>>

In order to accommodate potentially thousands of vehicles simultaneously flying in the air, additional structure is needed to allow for tractable analysis and intuitive monitoring. An air highway system on which platoons of vehicles travel accomplishes both goals. However, many details of such a concept need to be addressed. Due to the flexibility of placing air highways compared to building ground highways in terms of highway location, even the problem of air highway placement can be a daunting task. To address this, in the first part of this paper, we propose a flexible and computationally efficient way based on \cite{Sethian96} to perform optimal air highway replacement given an arbitrary cost map that captures the desirability of having UAVs fly over any geographical location. We demonstrate our method using the San Francisco Bay Area as an example. Once air highways are in place, platoons of UAVs can then fly in fixed formations along the highway to get from origin to destination.

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_form.tex
no message

\noindent where $x$ represents the state, and $u$ represents the control action. The techniques we present in this paper do not depend on the dynamics of the vehicles. However, for concreteness, we consider assume that the UAVs are quadrotors that fly at a constant altitude under non-faulty circumstances. For the quadrotor, we use a simple model in which the $x$ and $y$ dynamics are double integrators:

@@

\subsubsection{Vehicles as Hybrid Systems}
We model each vehicle as a hybrid system \cite{Lygeros98,Lygeros12} consisting of the modes "Free", "Leader", "Follower", and "Faulty". Within each mode, a set of maneuvers is available to allow the vehicle to change modes if desired. The modes and maneuvers are as follows:

@@

A Follower vehicle is a vehicle that is following a platoon leader. The Available maneuvers and mode transitions are

\begin{itemize}
\item remain a Follower by staying a distance of $b$ behind the vehicle in front in the current platoon,
\item become a Leader by splitting from the current platoon, and
\item become a Free vehicle by leaving the highway.
\end{itemize}

@@

If a vehicle from any of the other modes malfunction, it transitions into the Faulty mode and descends after some pre-specified duration $t_\text{faulty}$.
\end{itemize}

@@

For convenience, let $\vehSCS{i}$ denote the set of indices of vehicles with respect to which $Q_i$ checks safety against. If vehicle $\veh{i}$ is in a free vehicle, then it must check for safety with respect to all other vehicles, $\vehSCS{i} = \{j: j\neq i\}$. If the vehicle is part of a platoon, then it checks safety with respect to the platoon member in front and behind, $\vehSCS{i} = \{P_{j+1}, P_{j-1}\}$. Figure \ref{fig:vehicleNotation} summarizes the the indexing system of the vehicles.

@@

\begin{itemize}
\item merge onto a highway to form a platoon,
\item join a new or different platoon,
\item leave a platoon to create a new one,
\item reacting to a malfunctioning or intruder vehicles.
\end{itemize}

>>>>

\noindent where $x$ represents the state, and $u$ represents the control action. The techniques we present in this paper do not depend on the dynamics of the vehicles. However, for concreteness, we assume that the UAVs are quadrotors that fly at a constant altitude under non-faulty circumstances. For the quadrotor, we use a simple model in which the $x$ and $y$ dynamics are double integrators:

@@

\subsubsection{Vehicles as Hybrid Systems}
We model each vehicle as a hybrid system \cite{Lygeros98,Lygeros12} consisting of the modes ``Free", ``Leader", ``Follower", and ``Faulty". Within each mode, a set of maneuvers is available to allow the vehicle to change modes if desired. The modes and maneuvers are as follows:

@@

A Follower vehicle is a vehicle that is following a platoon leader. The available maneuvers and mode transitions are

\begin{itemize}
\item remain a Follower by staying a distance of $d_\text{sep}$ behind the vehicle in front in the current platoon,
\item become a Leader by splitting from the current platoon, and
\item become a Free vehicle by leaving the highway.
\end{itemize}

@@

If a vehicle from any of the other modes malfunctions, it transitions into the Faulty mode and descends after some pre-specified duration $t_\text{faulty}$.
\end{itemize}

@@

For convenience, let $\vehSCS{i}$ denote the set of indices of vehicles with respect to which $Q_i$ checks safety against. If vehicle $\veh{i}$ is a free vehicle, then it must check for safety with respect to all other vehicles, $\vehSCS{i} = \{j: j\neq i\}$. If the vehicle is part of a platoon, then it checks safety with respect to the platoon member in front and behind, $\vehSCS{i} = \{P_{j+1}, P_{j-1}\}$. Figure \ref{fig:vehicleNotation} summarizes the the indexing system of the vehicles.

@@

\begin{itemize}
\item merge onto a highway to form a platoon,
\item join a new or different platoon,
\item leave a platoon to create a new one,
\item reacting to malfunctioning or intruder vehicles.
\end{itemize}

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_reach.tex
no message

For our application, we will use a several decoupled system models and utilize the decoupled HJ formulation in \cite{Chen15}, which enables real time 4D reachable set computations and tractable 6D reachable set computations.

>>>>

For our application, we will use several decoupled system models and utilize the decoupled HJ formulation in \cite{Chen15}, which enables real time 4D reachable set computations and tractable 6D reachable set computations.

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_sim.tex
no message

\subsubsection{Forming a Platoon}
We first consider the scenario in which Free vehicles merge onto an initially unoccupied highway. In order to do this, each vehicle first checks for safety with respect to all other vehicles, and uses the safety controller if necessary, according to Section \ref{sec:reach_ctrl}\ref{sec:collision_ctrl}. Otherwise, the vehicle uses the liveness controller for getting to an absolute target set described in Section \ref{sec:reach_ctrl}\ref{sec:abs_target_ctrl} in order to merge onto the highway, create a platoon, and become a Leader vehicle if there are no platoons on the highway. If there is already a platoon on the highway, then the vehicle would use the liveness controller for getting to a target set relative to the platoon leader as described in Section \ref{sec:reach_ctrl}\ref{sec:rel_target_ctrl} to join the platoon and become a Follower.

@@

For $\veh{1}$ (red), an arbitrary point of entry on the highway is chosen as the target absolute position, and the velocity corresponding to a speed of $10$ in the direction of the highway is chosen as the target absolute velocity. This forms the target state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, from which we define the target set $\mathcal{L}_H$ as in Section \ref{sec:reach_ctrl}\ref{sec:abs_target_ctrl}.

@@

After completing merging onto the empty highway, $\veh{1}$ (red) creates a platoon and becomes its leader, while subsequent vehicles begin to form a platoon behind the leader in the order of ascending distance to $\veh{1}$ (red) according to the process described in Section \ref{sec:reach_ctrl}\ref{sec:rel_target_ctrl}. Here, we choose the target relative position $(\bar{p}_{x,r}, \bar{p}_{y,r})$ to be a distance $b$ behind the last reserved slot in the platoon, and the target relative velocity $(\bar{v}_{x,r}, \bar{v}_{y,r}) = (0,0)$ with respect to the leader in order to maintain the platoon formation. This gives us the target set $\mathcal{L}_P$ that we need.

@@

The $t=8.2$ shows the two platoons of vehicles traveling on the two air highways. One platoon has three vehicles, and the other has four vehicles. At $t=12.3$, the yellow vehicle begins steering off its original highway in order to join the other platoon. In terms of the hybrid systems modes, the yellow vehicle transitions from the Leader mode to the Follower mode. At the same time, the green vehicle transitions from the Follower mode to the Leader mode, since the previous platoon leader, the yellow vehicle, has left the platoon. By $t=16.9$, the yellow vehicle successfully changes highways and is now a follower in its new platoon.

>>>>

\subsubsection{Forming a Platoon}
We first consider the scenario in which Free vehicles merge onto an initially unoccupied highway. In order to do this, each vehicle first checks for safety with respect to all other vehicles, and uses the safety controller if necessary, according to Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:collision_ctrl}. Otherwise, the vehicle uses the liveness controller for getting to an absolute target set described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl} in order to merge onto the highway, create a platoon, and become a Leader vehicle if there are no platoons on the highway. If there is already a platoon on the highway, then the vehicle would use the liveness controller for getting to a target set relative to the platoon leader as described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:rel_target_ctrl} to join the platoon and become a Follower.

@@

For $\veh{1}$ (red), an arbitrary point of entry on the highway is chosen as the target absolute position, and the velocity corresponding to a speed of $10$ in the direction of the highway is chosen as the target absolute velocity. This forms the target state $\bar{x}_H=(\bar{p}_x, \bar{v}_x, \bar{p}_y, \bar{v}_y)$, from which we define the target set $\mathcal{L}_H$ as in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl}.

@@

After completing merging onto the empty highway, $\veh{1}$ (red) creates a platoon and becomes its leader, while subsequent vehicles begin to form a platoon behind the leader in the order of ascending distance to $\veh{1}$ (red) according to the process described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:rel_target_ctrl}. Here, we choose the target relative position $(\bar{p}_{x,r}, \bar{p}_{y,r})$ to be a distance $b$ behind the last reserved slot in the platoon, and the target relative velocity $(\bar{v}_{x,r}, \bar{v}_{y,r}) = (0,0)$ with respect to the leader in order to maintain the platoon formation. This gives us the target set $\mathcal{L}_P$ that we need.

@@

The $t=8.2$ plot shows the two platoons of vehicles traveling on the two air highways. One platoon has three vehicles, and the other has four vehicles. At $t=12.3$, the yellow vehicle begins steering off its original highway in order to join the other platoon. In terms of the hybrid systems modes, the yellow vehicle transitions from the Leader mode to the Follower mode. At the same time, the green vehicle transitions from the Follower mode to the Leader mode, since the previous platoon leader, the yellow vehicle, has left the platoon. By $t=16.9$, the yellow vehicle successfully changes highways and is now a follower in its new platoon.

### 2016-03-03 docs/AIAA 2016 highway platooning/arXiv_v1/plat_summary.tex
no message

% !TEX root = main.tex
\subsection{Summary of Controllers}
We have introduced several reachability-based controllers, as well as some simple controllers. Pair wise collision avoidance is guaranteed using the safety controller, described in Section \ref{sec:collision_ctrl}. As long as a vehicle is not in potential danger according to the safety reachable sets, it is free to use any other controller. All of these other controllers and their corresponding mode transitions are shown in Figure \ref{fig:modeControllers}.

The controller for getting to an absolute target state, described in Section \ref{sec:abs_target_ctrl}, is used whenever a vehicle needs to move onto a highway to become a platoon leader. This controller guarantees the success of the mode transitions shown in blue in Figure \ref{fig:modeControllers}.

The controller for getting to a relative target state, described in Section \ref{sec:rel_target_ctrl}, is used whenever a vehicle needs to join a platoon to become a follower. This controller guarantees the success of the mode transitions shown in green in Figure \ref{fig:modeControllers}.

For the simple maneuvers of traveling along a highway or following a platoon, many simple controllers such as the ones suggested in Section \ref{sec:other_ctrl} can be used. These controllers keep the vehicles in either the Leader or the Follower mode. Alternatively, additional controllers can be designed for exiting the highway, although these are not considered in this paper. All of these non-reachability-based controllers are shown in gray in Figure \ref{fig:modeControllers}.

>>>>

% !TEX root = main.tex
\subsection{Summary of Controllers}
We have introduced several reachability-based controllers, as well as some simple controllers. Pair-wise collision avoidance is guaranteed using the safety controller, described in Section \ref{sec:collision_ctrl}. As long as a vehicle is not in potential danger according to the safety reachable sets, it is free to use any other controller. All of these other controllers and their corresponding mode transitions are shown in Figure \ref{fig:modeControllers}.

The controller for getting to an absolute target state, described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:abs_target_ctrl}, is used whenever a vehicle needs to move onto a highway to become a platoon leader. This controller guarantees the success of the mode transitions shown in blue in Figure \ref{fig:modeControllers}.

The controller for getting to a relative target state, described in Section \ref{sec:platooning}-\ref{sec:reach_ctrl}-\ref{sec:rel_target_ctrl}, is used whenever a vehicle needs to join a platoon to become a follower. This controller guarantees the success of the mode transitions shown in green in Figure \ref{fig:modeControllers}.

For the simple maneuvers of traveling along a highway or following a platoon, many simple controllers such as the ones suggested in Section \ref{sec:platooning}-\ref{sec:other_ctrl} can be used. These controllers keep the vehicles in either the Leader or the Follower mode. Alternatively, additional controllers can be designed for exiting the highway, although these are not considered in this paper. All of these non-reachability-based controllers are shown in gray in Figure \ref{fig:modeControllers}.

### 2016-03-03 docs/AIAA 2016 highway platooning/high_waypoints.tex
no message

% !TEX root = main.tex
\subsection{From Paths to Waypoints}
Each of the cost-minimizing paths $\ppath_i$ computed from the solution to the Eikonal equation consists of a continuous set of points. Each path $\ppath_i$ is an approximation to the sequence of highways $\hws_{N_i}^i = \{\hw^i_j\}_{i=1,j=1}^{i=M,j=N_i}$ defined in \eqref{eq:ahpp}, but now indexed by the corresponding path index $i$. The

@@

To sparsify the continuous set of points on each path, we start at the destination point and note the path's heading. We add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$, and repeat this process is repeated along the entire path.

@@

To the collection of points resulting from the above process generates we add the origin and destination points to the collection. Repeating the entire process for every path, we waypoints for all the cost-minimizing paths under consideration. Figure \ref{fig:hw_ill} summarizes the entire air highway placement process.

>>>>

% !TEX root = main.tex
\subsection{From Paths to Waypoints}
Each of the cost-minimizing paths $\ppath_i$ computed from the solution to the Eikonal equation consists of a continuous set of points. Each path $\ppath_i$ is an approximation to the sequence of highways $\hws_{N_i}^i = \{\hw^i_j\}_{i=1,j=1}^{i=M,j=N_i}$ defined in \eqref{eq:ahpp}, but now indexed by the corresponding path index $i$.

@@

To sparsify the continuous set of points on each path, we start at the destination point and note the path's heading. We add to the collection of waypoints the first point on the path at which the heading changes by some threshold $\theta_C$, and repeat this process along the entire path.

@@

To the collection of points resulting from the above process, we add the origin and destination points. Repeating the entire process for every path, we obtain waypoints for all the cost-minimizing paths under consideration. Figure \ref{fig:hw_ill} summarizes the entire air highway placement process.

### 2016-03-03 docs/AIAA 2016 highway platooning/main.tex
no message

\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, aerial surveillance, and disaster response. As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the air space, in order to ensure their liveness and safety requirements are met. Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers are unrestricted. In this paper, we propose to have platoons of UAVs flying on air highways in order to impose the air space structure that allows for tractable analysis and intuitive monitoring. For the air highway placement problem, we use the flexible and efficient fast marching method to solve the Eikonal equation, which produces a sequence of air highways that minimizes the cost of flying from an origin to any destination. Within the platoons that travel on the air highways, we model each vehicle as a hybrid system with modes corresponding to its role in the platoon. Using HJ reachability, we propose several liveness controllers and a safety controller that guarantees the success and safety of all mode transitions. For a single altitude range, our approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges. We demonstrate the satisfaction of liveness and safety requirements through simulations of three common scenarios.}

@@

\section*{Nomenclature}
(Nomenclature entries should have the units identified)\\
\noindent\begin{tabular}{@{}lcl@{}}
$\cmap$ &=& Cost map \\
$\ccost$ &=& Cumulative cost of a path \\
$\ocost$ &=& Optimal cumulative cost of a path \\
$\hw$ &=& Air highway \\
$\hwd$ &=& Direction of travel of air highway \\
$\hws$ &=& A sequence of air highways \\
$\wpt$ &=& Waypoint \\
$x$ &=& System state (of a vehicle) \\
$\pos=(\pos_x, \pos_y)$ &=& Horizontal position \\
$\vel=(\vel_x, \vel_y)$ &=& Horizontal velocity \\
$\td$ &=& Time limit for descent during potential conflict \\
$\veh{i}$ &=& $i$th vehicle \\
$\vehSCS{i}$ &=& Set of vehicles to consider for safety for vehicle $i$
\end{tabular} \\

>>>>

\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations such as package delivery, aerial surveillance, and disaster response. As a result, UAV traffic management systems are needed to support potentially thousands of UAVs flying simultaneously in the air space, in order to ensure their liveness and safety requirements are met. Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers are unrestricted. In this paper, we propose to have platoons of UAVs flying on air highways in order to impose the air space structure that allows for tractable analysis and intuitive monitoring. For the air highway placement problem, we use the flexible and efficient fast marching method to solve the Eikonal equation, which produces a sequence of air highways that minimizes the cost of flying from an origin to any destination. Within the platoons that travel on the air highways, we model each vehicle as a hybrid system with modes corresponding to its role in the platoon. Using Hamilton-Jacobi reachability, we propose several liveness controllers and a safety controller that guarantee the success and safety of all mode transitions. For a single altitude range, our approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges. We demonstrate the satisfaction of liveness and safety requirements through simulations of three common scenarios.}

@@

\section*{Nomenclature}
(Nomenclature entries should have the units identified)\\
\noindent\begin{tabular}{@{}lcl@{}}
$\cmap$ &=& Cost map \\
$\ccost$ &=& Cumulative cost of a path \\
$\ocost$ &=& Optimal cumulative cost of a path \\
$\hw$ &=& Air highway \\
$\hwd$ &=& Direction of travel of air highway \\
$\hws$ &=& A sequence of air highways \\
$\wpt$ &=& Waypoint \\
$x$ &=& System state (of a vehicle) \\
$\pos=(\pos_x, \pos_y)$ &=& Horizontal position \\
$\vel=(\vel_x, \vel_y)$ &=& Horizontal velocity \\
$\td$ &=& Time limit for descent during potential conflict \\
$\veh{i}$ &=& $i$th vehicle \\
$\vehSCS{i}$ &=& Set of vehicles for vehicle $i$ to consider for safety 
\end{tabular} \\

### 2016-03-03 docs/AIAA 2016 highway platooning/plat_controllers.tex
no message

In both of the above cases, we use the dynamics of a single vehicle specified in \ref{eq:dyn}. The target state would be a position $(\Pos_x, \Pos_y)$ representing the desired merging point on the highway, along with a velocity $(\Vel_x, \Vel_y)$ that corresponds to the speed and direction of travel specified by the highway. For the reachability computation, we define the target set to be a small range of states around the target state $x_H = (\Pos_x, \Pos_y, \Vel_x, \Vel_y)$:

\begin{equation}
\begin{aligned}
\mathcal{L}_H = \{x: |\pos_x-\Pos_x|\le r_{\pos_x}, |v_x-\Vel_x|\le r_{\vel_x}, \\
|\pos_y - \Pos_y| \le r_{\pos_y}, |v_y - \Vel_y|\le r_{v\vel_y} \}.
\end{aligned}
\end{equation}

Here, we represent the target set $\mathcal{L}_H$ as the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE that we need to solve. Once the HJB PDE is solved, we obtain the reachable set from the subzero level set of the solution $V_H(t,x)$: $\mathcal V_H(t)$. More concretely, $\mathcal{V}_H(T) = \{x: V_H(-T,x)\le 0\}$ is the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$.

@@

To construct a controller for getting to a state relative to another vehicle, we use the relative dynamics of two vehicles, given in \ref{eq:rel_dyn}. In general, the target state is specified to be some position $(\Pos_{x,r}, \Pos_{y,r}$ and velocity $(\Vel_{x,r}, \Vel_{y,r})$ relative to a reference vehicle. In the case of a vehicle joining a platoon that maintains a single file, the reference vehicle would be the platoon leader, the desired relative position would be a certain distance behind the leader, depending on how many other vehicles are already in the platoon, and the desired relative velocity would be $(0,0)$ so that the formation can be kept.

For the reachability problem, we define the target set to be a small range of states around the target state $x_P = (\Pos_{x,r}, \Pos_{y,r}, \Vel_{x,r}, \Vel_{y,r}$:

@@

$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety against. We discuss $\mathcal{Q}(i)$ in Section \ref{subsec:safety_guarantees}.

\item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:

>>>>

In both of the above cases, we use the dynamics of a single vehicle specified in \eqref{eq:dyn}. The target state would be a position $(\Pos_x, \Pos_y)$ representing the desired merging point on the highway, along with a velocity $(\Vel_x, \Vel_y)$ that corresponds to the speed and direction of travel specified by the highway. For the reachability computation, we define the target set to be a small range of states around the target state $x_H = (\Pos_x, \Pos_y, \Vel_x, \Vel_y)$:

\begin{equation}
\begin{aligned}
\mathcal{L}_H = \{x: |\pos_x-\Pos_x|\le r_{\pos_x}, |v_x-\Vel_x|\le r_{\vel_x}, \\
|\pos_y - \Pos_y| \le r_{\pos_y}, |v_y - \Vel_y|\le r_{\vel_y} \}.
\end{aligned}
\end{equation}

Here, we represent the target set $\mathcal{L}_H$ as the zero sublevel set of the function $l_H(x)$, which specifies the terminal condition of the HJB PDE that we need to solve. Once the HJB PDE is solved, we obtain the reachable set $\mathcal V_H(t)$ from the subzero level set of the solution $V_H(t,x)$. More concretely, $\mathcal{V}_H(T) = \{x: V_H(-T,x)\le 0\}$ is the set of states from which the system can be driven to the target $\mathcal{L}_H$ within a duration of $T$.

@@

To construct a controller for getting to a state relative to another vehicle, we use the relative dynamics of two vehicles, given in \eqref{eq:rel_dyn}. In general, the target state is specified to be some position $(\Pos_{x,r}, \Pos_{y,r})$ and velocity $(\Vel_{x,r}, \Vel_{y,r})$ relative to a reference vehicle. In the case of a vehicle joining a platoon that maintains a single file, the reference vehicle would be the platoon leader, the desired relative position would be a certain distance behind the leader, depending on how many other vehicles are already in the platoon, and the desired relative velocity would be $(0,0)$ so that the formation can be kept.

For the reachability problem, we define the target set to be a small range of states around the target state $x_P = (\Pos_{x,r}, \Pos_{y,r}, \Vel_{x,r}, \Vel_{y,r})$:

@@

$\mathcal{Q}(i)$ is the set of quadrotors with which quadrotor $i$ checks safety against.
\item Use the safety or liveness controller depending on the values $V_S(-t,x_i-x_j),j\in \mathcal{Q}(i)$:

### 2016-03-03 docs/CDC 2015 platooning/arXiv/conclusion.tex
no message

% !TEX root = platooning.tex
\section{Conclusions and Future Work}
We considered single-file platoons of UAVs modeled by hybrid systems traveling along air highways. Using HJ reachability, we proposed liveness controllers and wrapped a safety controller around them to ensure no collision can occur from a single safety breach. Additional safety breaches can be handled by multiple altitude ranges in the airspace. Our simulations show that by putting vehicles into single-file platoons, the likelihood of having multiple safety breaches is low, and conflicts involving a single malfunctioning UAV or intruder can be resolved in a single altitude level.

>>>>

% !TEX root = platooning.tex
\section{Conclusions and Future Work}
We considered single-file platoons of UAVs modeled by hybrid systems traveling along air highways. Using HJ reachability, we proposed liveness controllers for merging onto highways and merging into existing platoons, and wrapped a safety controller around liveness controllers to ensure no collision between the UAVs can occur. Under the assumption that faulty vehicles can descend after a pre-specified duration, our safety controller guarantees that no collisions will occur in a single altitude level as long as at most one safety breach occurs for each vehicle in the platoon. Additional safety breaches can be handled by multiple altitude ranges in the airspace. Our simulations show that by putting vehicles into single-file platoons, the likelihood of having multiple safety breaches is low, and conflicts involving a single malfunctioning UAV or intruder can be resolved in a single altitude level.

Immediate future work includes exploring different vehicle models, investigating algorithms for resolving multiple safety breaches within the same altitude, and more broadly related problems such as airspace structure and air highway placement.
